%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {NCR Voyix}{Oct 2020 -- Present}
    {Lead Software Developer}{Bengaluru, India}
    
    {\vspace{.5em}\footnotesize\emph{Technologies: Java, Spring, Spring Batch, Microservices, Webservices, JUnit, Mockito, Docker, Kubernetes, Google Cloud (GCP), APIGEE, Swagger Editor, Maven, JavaScript, React JS, MySQL, Shell Scripting, Git.}}
    \resumeItemListStart
        \resumeItem{Designed and implemented a scalable microservices architecture using
        Java and Spring Boot, resulting in improved system performance and the ability to handle increased user load.}
        \resumeItem{Developed and optimized complex spring batch jobs to process large
        volumes of transactions from diverse systems, achieving a 30\% reduction in processing time and ensuring data integrity.}
        \resumeItem{Collaborated closely with the Site Reliability Engineering team to
        migrate on-premises virtual machines to the cloud, achieving a 40\% reduction in infrastructure maintenance costs and enabling automated deployment and scaling.}
        \resumeItem{Contributed to the development of responsive and intuitive user interfaces using React JS, which led to a 25\% reduction in bounce rates and a 15\% increase in user engagement, significantly improving overall user satisfaction.}
        \resumeItem{Engaged in architectural discussions, offering technical guidance to the development team, leading to a 20\% improvement in adherence to best practices and a significant enhancement in overall code quality.}
        \resumeItem{Conducted code reviews, refactoring, and performance optimization to enhance system reliability, maintainability, and scalability.}
        \resumeItem{Collaborated with QA engineers to establish comprehensive test strategies, reducing defects by 20\% and ensuring high software quality.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Fair Isaac Corporation}{Jan 2018 -- Oct 2020}
    {Senior Solution Consultant}{Bengaluru, India}

    {\vspace{.5em}\footnotesize\emph{Technologies: Java, Spring, Maven, Microservices, Webservices, JUnit, Mockito, MySQL.}}
    \resumeItemListStart
        \resumeItem{Led the implementation of microservices architecture in the Google
        Cloud environment, leveraging cloud technologies to enhance scalability and performance.}
        \resumeItem{Implemented robust security measures, reducing security incidents by 25\% through enhanced authentication and authorization mechanisms, ensuring the protection of sensitive user data.}
        \resumeItem{Crafted software components with a test-driven methodology, achieving 95\% code coverage using JUnit for comprehensive unit testing and functionality validation.}
        \resumeItem{Engaged with QA professionals, actively contributing to defect triage and resolution processes, leading to a significant improvement in software stability.}
        \resumeItem{Participated in the adoption of agile methodologies, utilizing Jira and Confluence, improving team productivity through iterative development cycles.}
    \resumeItemListEnd

    \resumeSubheading
    {Siemens}{Oct 2015 -- Aug 2017}
    {Senior System Engineer}{Bengaluru, India}

     {\vspace{.5em}\footnotesize\emph{Technologies: Java, Spring, Maven, Webservices, JUnit, Selenium, MySQL.}}
    \resumeItemListStart
        \resumeItem{Architected highly scalable microservices using Spring Boot, ensuring
        optimal performance and responsiveness of the application.}
        \resumeItem{Architected and executed a Selenium-based test automation framework, resulting in a 80\% reduction in testing process time and effort.}
        \resumeItem{Led rigorous testing of microservices and Restful web services, achieving a 95\% pass rate in functional, integration, and performance tests, ensuring elevated reliability and quality standards.}
        \resumeItem{Applied industry best practices and coding standards, yielding a 15\% improvement in code maintainability and scalability for microservices and test automation frameworks.}
    \resumeItemListEnd

    \resumeSubheading
    {SLK Software}{Jul 2013 -- Sep 2015}
    {Software Engineer}{Bengaluru, India}

    {\vspace{.5em}\footnotesize\emph{Technologies: Java, Spring, EJB, JUnit.}}
    \resumeItemListStart
        \resumeItem{Actively participated in technical planning sessions, providing insights and contributing to solving complex tasks.}
        \resumeItem{Maintained detailed documentation of issue resolutions and best
        practices, facilitating knowledge transfer and continuous improvement
        within the development team.}
        \resumeItem{Diagnosed and resolved reported issues, ensuring prompt solutions through effective stakeholder engagement.}
        \resumeItem{Formulated extensive JUnit test cases, resulting in a 20\% reduction in post-deployment issues by identifying and addressing potential issues early in the development cycle.}
    \resumeItemListEnd

\resumeSubHeadingListEnd